The Holy Hand Grenade of Antioch

### 2020-02-22 draft-camelot-holy-grenade.tex
feat: enable monospace, superscript and subscript examples

The participants of that renowned exercise in cross-cultural
communication, to wit the exchange between the
\textit{Knights of the Round Table}
and the taunting French soldiers serving under 
\textbf{Guy de Lombard} are,
% TODO: properly speaking, outside the scope of this `menagerie`, being more
% TODO: or less human. Notwithstanding, several^ish^ beasts both animate~d~
and wooden played a significant part in this encounter; most
notably:

>>>>

The participants of that renowned exercise in cross-cultural
communication, to wit the exchange between the
\textit{Knights of the Round Table}
and the taunting French soldiers serving under 
\textbf{Guy de Lombard} are,
properly speaking, outside the scope of this \texttt{menagerie}, being more
or less human. Notwithstanding, several\textsuperscript{ish} beasts both animate\textsubscript{d}
and wooden played a significant part in this encounter; most
notably:
